\section{Presentation}
I am an electronic engineer from School of Engineering and Technology ITBA,
recently received as Specialist in Embedded Systems and studying a
Master in Embedded Systems from University of Buenos Aires, UBA.\\
I developed my career working in the area of product development of several
national companies and in the area of research in state institutions.\\
I was in charge of an electronic engineering studio offering electronic design
and production services and I am currently working as a freelance electronic
developer with the possibility of issuing 'A' and 'B' invoices.\\
I work daily designing embedded electronic equipment executing tasks such as: \\
\cvlistitem{Taking requirements and planning acceptance tests of hard and soft.}
\cvlistitem{Schematic design, PCB, simulations, assembly, 3D modeling and machining.}
\cvlistitem{Coding for real time in C / C ++ in bare metal or on RTOS.}
\cvlistitem{Codification and execution of the unit tests and management of continuous integration tools.}
\cvlistitem{Assembly and start-up of prototypes and documentation for the assembly line.}
I am very pragmatic, committed and enjoy solving complex problems in a creative way by exchanging ideas
with my peers I prefer down-top developments using agile concepts to keep the product functional from
the beggining.\\
I have an electronics workshop with tools such as:\\
\cvlistitem{Assembly line of SMD and TH plates, pasta stencil, pick and place, reflow oven and wave soldering machine.}
\cvlistitem{Reworking and manual welding tools.}
\cvlistitem{Stock of SMD and TH materials of current and specific use.}
\cvlistitem{CNC machining center.}
\cvlistitem{Machine for cutting and laser engraving.}
\cvlistitem{Several machines for 3D printing.}
\cvlistitem{Generators, Oscilloscopes and Advanced Instrumentation for measurement and diagnosis.}
\cvlistitem{Electronic tools for firmware development.}
These tools, my experience, technical ability and frequent academic updating allow me to unwrap
in most instances of the development of a professional embedded electronic equipment.\\
