\section{Works and Publications}
\cventry { 2021 }{ Visual alignment using registration marks for a computer numerical controled machine CNC                                   }{ Embedded systems Magister, FIUBA                                                           }{ }{ }{ Final work of the magister course in embedded systems, Director: MEE. Ing. Norberto M. Lerendegui (IEEE) \href \linknkhackinforme                          { see material }, \href \linknkhackpresentacion     { see presentation      }, \href \linknkhackdefensa { see thesis defense }, \href \linknkhackvideos { see videos }, \href \linknkhackmaterialuba {see official material}}
\cventry { 2018 }{ Three Axis CNC Machine Controller                                                                                          }{ Embedded systems Specialization                                                            }{ }{ }{ Final work of the specialization course in embedded systems, Director: Ing. Juan Manuel Cruz             \href \linkcncinforme                             { see material }, \href \linkcncpresentacion        { see presentation      }, \href \linkcncdefensa    { see thesis defense }, \href \linkcncvideos    { see videos }, \href \linkcncmaterialuba    {see official material}}
\cventry { 2010 }{ Smoothing of images by inhomogeneous diffusion                                                                             }{ Biomedical image processing, UTN                                                           }{ }{ }{ Final work Processing of biomedical images, Tutor: Dr. Castro \href \linkbiomedicasfinal                                                                   { See material }.                                                           }
\cventry { 2008 }{ Study of photo thermal techniques applied to the measurement of gas flow.                                                  }{ CITEDEF                                                                                    }{ }{ }{ I was presented under the tutelage of Dr. Francisco Manzano and as goal of approval of Optoelectronics II. \href \linkcitefa                               { See material }.                                                           }
\cventry { 2004 }{ Design and implementation of a dynamic screen based on 3200 filament lamps with 16 gray scales and 20fps updatable by ftp. }{ LampMatrix, Thesis, ITBA                                                                   }{ }{ }{ Under the tutelage of Professor Villamil, an advertising screen based on filament lamps was designed and manufactured entirely. \href \linklampmatrixvideo { See video    }, \href \linklampmatrixinforme   { See material             }.                                            }
\cventry { 2003 }{ Design and Simulation of a pipeline-structured Floating Point Unit for high performance general purpose processors         }{ JAIIO 32\textsuperscript{ th }Argentine Conference on Informatics and Operational Research }{ }{ }{ \href \linkjaiio                           { See material }.                                            }
\cventry { 2003 }{ Selection of the Optimum Stage Number in Pipelined Floating-Point Units                                                    }{ CACIC, Argentine Congress of Computer Science                                              }{                                                            }{ }{ \href \linkcacic                                                                                                                                           { See material }                                                            }

